---
title: "phenoRep_WorkingCode"
author: "K. Duffy"
date: "11/2/2018"
output: html_document
---
Load libraries
```{r setup, include=FALSE}
library(sp)
library(ncdf4)
library(rvest)
library(raster)
library(jsonlite)
library(rgdal)
```

Grab PhenoCam data via API:
```{r}
c      = jsonlite::fromJSON('https://phenocam.sr.unh.edu/api/cameras/?format=json&limit=2000')
c = c$results
c_m=c$sitemetadata #the metadata is a little messy as it's nested, so I fixed that here:
c$sitemetadata=NULL
cams_=cbind(c, c_m)
cams_[is.na(cams_)] = 'N'
```

Here's a PFT key to reclassify PhenoCam Primary veg to query MODIS landcover data:

```{r}
pft_key = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,254,255)
pft_abbreviated = c('Water','EN','EB','DN','DB','MF','SH','SH','SV','SV','GR','WL','AG','UB','MX','TN','UN','NAN','NAN')
pft_expanded = c('Water', 'Evergreen Needleleaf Forest', 'Evergreen Broadleaf Forest', 'Deciduous Needleleaf Forest', 'Deciduous Broadleaf Forest', 'Mixed Forest',
                 'Shrubland', 'Shrubland', 'Savanna', 'Savanna','Grassland', 'Wetland', 'Agriculture', 'Urban', 'Mixed Forest', 'Tundra', 'No Vegetation', 'Unclassified', 'Unclassified' )
pft_df = data.frame(pft_key,pft_abbreviated,pft_expanded)
```

Here's a cache of AppEEARS tasks for landcover, NDVI etc:
```{r}
# Load in dataframe with cached AppEEARS tasks
appeears_tasks     = readRDS(file = './AppEEARS_data/cache_df.df')
```

From here you would use the AppEEARS.R function to pull in the data.  The data is a series of netcdf files.  You'll just want the land cover classification for now.  Also, I've thrown up a whole US landcover if you want to think bigger :)

Here's a snippet of code if you want to just clip from the larger entire US geotiff:
```{r}
# Creates boundary box for clipping rasters using lat/lon from phenocam site
#where lat and lon could be extracted from the PhenoCam API metadata df above, and r is the raster or geotiff that you want to work with.
#Where primary is equal to the primary vegetation type from the phenocam API metadata df
#Reclassify selects a match between the phenocam primary vegetation and the raster/geotiff vegetation.  You could probably simplify this a bit, it's lifted from our PhenoSynth shiny r interface so it had to be reactive
crop_raster = function(lat_, lon_, r_, reclassify=FALSE, primary=NULL){
  height = .03
  width  = .05
  e      = as(extent(lon_-width, lon_ + width, lat_ - height, lat_ + height), 'SpatialPolygons')
  crs(e) <- "+proj=longlat +datum=WGS84 +no_defs"
  r        = raster::crop(r_, e, snap='near')
  
  if (reclassify == FALSE){
    return (r)
    
  }else if (reclassify == TRUE){
    
    water = 17*2
    
    m = c(1,2,
          2,2,
          3,2,
          4,2,
          5,2,
          6,2,
          7,2,
          8,2,
          9,2,
          10,2,
          11,2,
          12,2,
          13,2,
          14,2,
          15,2,
          16,2,
          17,2)
    
    if(!is.null(primary)){
      prim    = primary*2
      m[prim] = 1
    }
    
    rclmat = matrix(m, ncol=2, byrow=TRUE)
    rc     = raster::reclassify(r, rclmat)
    if (length(unique(values(rc))) == 1){
      
      m = c(1,NA,
            2,NA,
            3,NA,
            4,NA,
            5,NA,
            6,NA,
            7,NA,
            8,NA,
            9,NA,
            10,NA,
            11,NA,
            12,NA,
            13,NA,
            14,NA,
            15,NA,
            16,NA,
            17,NA)
      
      rclmat = matrix(m, ncol=2, byrow=TRUE)
      rc     = raster::reclassify(r, rclmat)
    }
    return (rc)
  }
}
```